\documentclass[10pt, oneside]{article}%{amsart}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{fullpage}

%SetFonts

%SetFonts


\title{Dr. Wayne O. Cochran}
\author{Computer Scientist\\
       %Software Engineer\\
       Intel Sports, Intel Corporation\\
       %(360) 334-0200 (cell) \\
       {\tt wayne.cochran@intel.com}}
\date{\vspace{-5ex}}

\begin{document}
\thispagestyle{empty}
\maketitle
\thispagestyle{empty}

\section*{Interests and Skills}

\begin{description}
\item[\bf Computer Graphics] : research and development, 
   fast rasterization and low level optimization, 
   3D pipeline design,  GPU shaders, 
   mathematical modeling, volumetric rendering, intricate fractal models.
\item[\bf General Purpose GPU Programming] : %Algorithm development, 
    image processing, 
    physics simulation, video stitching, CUDA.
\item[\bf Image Processing / Computer Vision] : geometric transformations, color processing, 
   camera models, image reconstruction, compositing, 
   %frequency encoding, image reconstruction, compression, % \ldots
%\item[\bf Low-Level Vision] : f
   feature detection, projective geometry, dense stereo matching, 
   belief propagation for solving Markov Random Fields, stereo calibration, OpenCV.
\item[\bf Numerical Computing] : Optimization techniques, %Bayesian Networks, 
   parallel algorithms, numerical analysis.
\end{description}

\section*{Professional Experience}
\begin{description}
\item[\bf Software Engineer] 2017 - present,
Intel Sports, Intel Corporation. 
Research, development and implementation of live video processing
pipeline that captures, transforms, projects,
rectifies, stitches, encodes, and transmits
large stereo panorama streams. Research and Development of point-cloud encoding
and rendering techniques.
\item[\bf Clinical Associate Professor] 1999-2017, 
Washington State University Vancouver.
Taught numerous courses at WSU that cover a wide
range of topics from the sophomore to graduate level that includes
Computer Graphics, Numerical Computing, Compiler Design, Theory of Computation.
%Operating Systems, and Computer Networks. 
%Research in intricate surface and texture
%modeling using recurrent fractal models. 
\item[\bf Software Engineer] 1990-1992,
Raster Graphics Inc. Design and implementation of rasterization firmware.
% for
%industrial graphics boards.
\end{description}

\section*{Education}
\begin{description}
\item[\bf Ph.D. Computer Science] 1998, Washington State University,
School of Electrical Engineering and Computer Science.
Dissertation Title: ``A Recurrent Modeling Toolset.''
\item[\bf M.S. Computer Science] 1994, Washington State University,
School of Electrical Engineering and Computer Science. Curtis Fellowship.
Thesis title: ``Fractal Volume Compression.''
\item[\bf B.S. Mathematics] cum laude, 1990.
University of Washington. 
Golden Key,
%National Honor Society, 
Dean's List, Phi Beta Kappa.
\end{description}

\enlargethispage{\baselineskip}

\section*{Selected Publications}
\begin{enumerate}
\item Matthew J. Lambert, Wayne O. Cochran. Kyle G. Olsen, Cynthia D. Cooper,
  Evidence for widespread subfunctionalization of splice forms in vertebrate genomes,
  {\em Genome Research.} 2015 May; 25(5): 624Ð632.
\item
Wayne O. Cochran, John C. Hart, Patrick J. Flynn,
Fractal Volume Compression,
{\em IEEE Transactions on Visualization and Computer Graphics}
December 1996.
\end{enumerate}

\end{document}  